Yeast Tandem Deamination Figure Generation

### 2022-06-08 R/YeastTandemDeaminationDataGeneration.rmd
Created yeast tandem deamination notebooks

---
title: "XP-C Tandem Deamination Data Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered]
  mismatchType:
    label: "Mismatch Type"
    value: CC>TT
    input: select
    choices: [CC>TT, GG>AA]
---

@@

cellType = "XP-C"
CPDTimepoints = list(`1h` = NULL)
sixFourTimepoints = list(`1h` = NULL)
expansionOffset = 10
minReadLength = 22; maxReadLength = 30

>>>>

---
title: "Yeast Tandem Deamination Data Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered]
  mismatchType:
    label: "Mismatch Type"
    value: CC>TT
    input: select
    choices: [CC>TT, GG>AA]
---

@@

expansionOffset = 10
cellType = "yeast"
CPDTimepoints = list(`5min` = NULL, `20min` = NULL, `1h` = NULL)
sixFourTimepoints = list(`5min` = NULL, `20min` = NULL)
minReadLength = 22; maxReadLength = 25

### 2022-06-08 R/YeastTandemDeaminationFigureGeneration.rmd
Created yeast tandem deamination notebooks

---
title: "XP-C Tandem Deamination Figure Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered]
  mismatchType:
    label: "Mismatch Type"
    value: CC>TT
    input: select
    choices: [CC>TT, GG>AA]
---

>>>>

---
title: "Yeast Tandem Deamination Figure Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered]
  mismatchType:
    label: "Mismatch Type"
    value: CC>TT
    input: select
    choices: [CC>TT, GG>AA]
---
